### 2021-10-28 documents/floats/go.tex
new autogenerated tables
fixed proto-pekodian 'to go'
regular verbs in data and docs
further revision of verbs section

\begin{table}
\centering
\caption[Reflexes of \rc{ɨtə(mə)} \qu{to go}]{Reflexes of \rc{ɨtə(mə)} \qu{to go} \parencites[291]{cruz2005fonologia}[292]{triomeira1999}[195]{wayanatavares2005}[87]{gildea1994akuriyo}{alves2017arara}[27, 248]{hixkaryanaderby1985}[45, 62]{waiwaihawkins1998}[54, 80]{ikpengpacheco2001}[112, 374]{von1892bakairi}[181, 216]{maquiritaricaceres2011}[112]{meira1998proto}[168]{hoff1968carib}[139]{meira2006syntactic}[4]{caceres2018yawarana}[74]{muller1975mapoyo}[198]{mattei1994diccionario}[48, 50]{macushiabbott1991}[172]{garcia2006diccionario}[6; p.c., Spike Gildea]{franchetto2002kuikuro}}
\label{tab:go}
\begin{tabular}[t]{@{}lllllll@{}}
\toprule
Language &             Form & \multicolumn{5}{l}{Alignment} \\
\midrule
\kaxui    &     \obj{to(mo)} &           &  t &  o &  m &  o \\
\hixka    &      \obj{(ɨ)to} &         ɨ &  t &  o &    &    \\
\waiwai   &   \obj{(e)to(m)} &         e &  t &  o &  m &    \\
\arara    &        \obj{ɨdo} &         ɨ &  d &  o &    &    \\
\ikpeng   &       \obj{aran} &         a &  r &  a &  n &    \\
\ikpeng   &        \obj{ero} &         e &  r &  o &    &    \\
\bakairi  &      \obj{(ɨ)tə} &         ɨ &  t &  ə &    &    \\
\trio     &      \obj{tə(n)} &           &  t &  ə &  n &    \\
\akuriyo  &  \obj{(ə)tə(mɨ)} &         ə &  t &  ə &  m &  ɨ \\
\carijo   &       \obj{təmə} &           &  t &  ə &  m &  ə \\
\wayana   &   \obj{(ɨ)tə(m)} &         ɨ &  t &  ə &  m &    \\
\kalina   &         \obj{to} &           &  t &  o &    &    \\
\kalina   &       \obj{(ɨ)ʔ} &         ɨ &  ʔ &    &    &    \\
\maqui    &    \obj{ɨtə(mə)} &         ɨ &  t &  ə &  m &  ə \\
\ingariko &        \obj{ətə} &         ə &  t &  ə &    &    \\
\pemon    &      \obj{(e)tə} &         e &  t &  ə &    &    \\
\macushi  &      \obj{(a)tɨ} &         a &  t &  ɨ &    &    \\
\panare   &      \obj{tə(n)} &           &  t &  ə &  n &    \\
\yawarana &         \obj{tə} &           &  t &  ə &    &    \\
\mapoyo   &         \obj{tə} &           &  t &  ə &    &    \\
\uxc      &      \obj{(e)te} &         e &  t &  e &    &    \\
\yukpa    &         \obj{to} &           &  t &  o &    &    \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Reflexes of \rc{ɨtə[mə]} \qu{to go}]{Reflexes of \rc{ɨtə[mə]} \qu{to go} \parencites[291]{cruz2005fonologia}[292]{triomeira1999}[195]{wayanatavares2005}[87]{gildea1994akuriyo}[153]{alves2017arara}[27, 248]{hixkaryanaderby1985}[45, 62]{waiwaihawkins1998}[54, 80]{ikpengpacheco2001}[112, 374]{von1892bakairi}[181, 216]{maquiritaricaceres2011}[112]{meira1998proto}[168]{hoff1968carib}[139]{meira2006syntactic}[4]{caceres2018yawarana}[74]{muller1975mapoyo}[198]{mattei1994diccionario}[48, 50]{macushiabbott1991}[172]{garcia2006diccionario}[6; p.c., Spike Gildea]{franchetto2002kuikuro}}
\label{tab:go}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
Language & \multicolumn{6}{l}{Form} \\
\midrule
\kaxui    &     \obj{to[mo]} &    &  t &  o &  m &  o \\
\hixka    &      \obj{[ɨ]to} &  ɨ &  t &  o &    &    \\
\waiwai   &   \obj{[e]to[m]} &  e &  t &  o &  m &    \\
\arara    &        \obj{ɨdo} &  ɨ &  d &  o &    &    \\
\ikpeng   &       \obj{aran} &  a &  r &  a &  n &    \\
\ikpeng   &        \obj{ero} &  e &  r &  o &    &    \\
\bakairi  &      \obj{[ɨ]tə} &  ɨ &  t &  ə &    &    \\
\trio     &      \obj{tə[n]} &    &  t &  ə &  n &    \\
\akuriyo  &  \obj{[ə]tə[mɨ]} &  ə &  t &  ə &  m &  ɨ \\
\carijo   &       \obj{təmə} &    &  t &  ə &  m &  ə \\
\wayana   &   \obj{[ɨ]tə[m]} &  ɨ &  t &  ə &  m &    \\
\kalina   &         \obj{to} &    &  t &  o &    &    \\
\kalina   &       \obj{[ɨ]ʔ} &  ɨ &  ʔ &    &    &    \\
\maqui    &    \obj{ɨtə[mə]} &  ɨ &  t &  ə &  m &  ə \\
\ingariko &        \obj{ətə} &  ə &  t &  ə &    &    \\
\pemon    &      \obj{[e]tə} &  e &  t &  ə &    &    \\
\macushi  &      \obj{[a]tɨ} &  a &  t &  ɨ &    &    \\
\panare   &      \obj{tə[n]} &    &  t &  ə &  n &    \\
\yawarana &         \obj{tə} &    &  t &  ə &    &    \\
\mapoyo   &         \obj{tə} &    &  t &  ə &    &    \\
\uxc      &      \obj{[e]te} &  e &  t &  e &    &    \\
\yukpa    &         \obj{to} &    &  t &  o &    &    \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-28 documents/floats/pwaireg.tex
further revision of verbs section

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[150]{howard2001wrought}[189, 190, 196]{hixkaryanaderby1985}[209, 211]{hawkins1953waiwai}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &     \qu{to fall} &      \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \obj{k-eɸurka-} &   \obj{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \obj{m-eɸurka-} &    \obj{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \obj{t-eɸurka-} &  \obj{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \obj{ɲ-eɸurka-} &   \obj{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[189, 190, 196]{hixkaryanaderby1985}[209, 211]{hawkins1953waiwai}[150]{howard2001wrought}[30]{waiwaihawkins1998}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &    \qu{to fall} &     \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \rc{k-eɸurka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &    \rc{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-28 documents/floats/say.tex
new autogenerated tables
regular verbs in data and docs
further revision of verbs section

\begin{table}
\centering
\caption[Reflexes of \rc{ka(ti)} \qu{to say}]{Reflexes of \rc{ka(ti)} \qu{to say} \parencites[4]{meira2003bakairi}[48]{franchetto2008absolutivo}[209]{ikpengpacheco2001}[153]{alves2017arara}[182]{hixkaryanaderby1985}[113]{meira1998proto}[107]{koehn1986apalai}[26]{waiwaihawkins1998}[66]{camargo2010wayana}[59]{macushiabbott1991}[123]{swiggers2010gramatica}[430]{courtz2008carib}[125]{akawaiocaesar2003}[102; p.c., Spike Gildea]{mattei1994diccionario}}
\label{tab:say}
\begin{tabular}[t]{@{}llllll@{}}
\toprule
Language &          Form & \multicolumn{4}{l}{Alignment} \\
\midrule
\kaxui   &   \obj{ka(s)} &         k &  a &  s &    \\
\hixka   &   \obj{ka(h)} &         k &  a &  h &    \\
\waiwai  &   \obj{ka(s)} &         k &  a &  s &    \\
\arara   &      \obj{ke} &         k &  e &    &    \\
\ikpeng  &      \obj{ke} &         k &  e &    &    \\
\bakairi &      \obj{ke} &         k &  e &    &    \\
\trio    &      \obj{ka} &         k &  a &    &    \\
\akuriyo &      \obj{ka} &         k &  a &    &    \\
\carijo  &      \obj{ka} &         k &  a &    &    \\
\wayana  &   \obj{ka(i)} &         k &  a &    &  i \\
\apalai  &  \obj{ka(ʃi)} &         k &  a &  ʃ &  i \\
\kalina  &      \obj{ka} &         k &  a &    &    \\
\kapon   &      \obj{ka} &         k &  a &    &    \\
\pemon   &      \obj{ka} &         k &  a &    &    \\
\macushi &      \obj{ka} &         k &  a &    &    \\
\panare  &   \obj{ka(h)} &         k &  a &  h &    \\
\uxc     &      \obj{ki} &         k &  i &    &    \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Reflexes of \rc{ka[ti]} \qu{to say}]{Reflexes of \rc{ka[ti]} \qu{to say} \parencites[4]{meira2003bakairi}[48]{franchetto2008absolutivo}[209]{ikpengpacheco2001}[153]{alves2017arara}[182]{hixkaryanaderby1985}[113]{meira1998proto}[107]{koehn1986apalai}[26]{waiwaihawkins1998}[66]{camargo2010wayana}[59]{macushiabbott1991}[123]{swiggers2010gramatica}[430]{courtz2008carib}[125]{akawaiocaesar2003}[102; p.c., Spike Gildea]{mattei1994diccionario}}
\label{tab:say}
\begin{tabular}[t]{@{}llllll@{}}
\mytoprule
Language & \multicolumn{5}{l}{Form} \\
\midrule
\kaxui   &   \obj{ka[s]} &  k &  a &  s &    \\
\hixka   &   \obj{ka[h]} &  k &  a &  h &    \\
\waiwai  &   \obj{ka[s]} &  k &  a &  s &    \\
\arara   &      \obj{ke} &  k &  e &    &    \\
\ikpeng  &      \obj{ke} &  k &  e &    &    \\
\bakairi &      \obj{ke} &  k &  e &    &    \\
\trio    &      \obj{ka} &  k &  a &    &    \\
\akuriyo &      \obj{ka} &  k &  a &    &    \\
\carijo  &      \obj{ka} &  k &  a &    &    \\
\wayana  &   \obj{ka[i]} &  k &  a &    &  i \\
\apalai  &  \obj{ka[ʃi]} &  k &  a &  ʃ &  i \\
\kalina  &      \obj{ka} &  k &  a &    &    \\
\kapon   &      \obj{ka} &  k &  a &    &    \\
\pemon   &      \obj{ka} &  k &  a &    &    \\
\macushi &      \obj{ka} &  k &  a &    &    \\
\panare  &   \obj{ka[h]} &  k &  a &  h &    \\
\uxc     &      \obj{ki} &  k &  i &    &    \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-28 documents/sections/extensions.tex
further revision of verbs section

The V-initial nature of \qu{to go} is evidenced in its Xinguan forms, while \bakairi \phon{\rc{wɨ}}{\obj{u}} resulted in a shift of the morpheme boundary (see also \cref{sec:go}).
The \ikpeng form \obj{aran} is compatible with our reconstruction \rc{ɨtən}, when one considers that \ikpeng \obj{a} is an attested outcome of \rc{ə}.\footnote{\begin{inlinelist}
 \item \obj{akari} \qu{dog} in \cref{tab:pxinw} above
 \item \obj{anma} \qu{path} \parencite[24]{ikpengpacheco2001} from \PC \rc{ətema} \parencite[12]{gildea2007greenberg}
 \item \obj{jaj} \qu{tree} \parencite[98]{ikpengpacheco2001} from \PC \rc{jəje}
 \end{inlinelist}.}
This attested change of \rc{ə} to \obj{a} need only be preceded by a assimilatory lowering of initial \rc{ɨ} to \rc{ə}, to yield the form \obj{aran} from \rc{ɨtən}.
Other \ikpeng reflexes of \qu{to go} offer evidence for the suggested intermediate stage \rc{\underline{ə}t\underline{ə}n}: \obj{\underline{e}r\underline{o}-lɨ} \qu{s/he went} \parencite[25]{ikpengpacheco2001}.

@@

\pex<car1w>\carijo \parencite[][5, 42]{guerrero2016karihona}
\a<car-24>
\begingl
\gla wɨ-tə-e=rehe//
\glb \gl{1}-go-\gl{npst}=\gl{frust}//
\glft \qu{I almost go (but I am not going to go).}//
\endgl
\a<car-25>
\begingl
\gla əji-marə-ne w-a-e//
\glb \gl{2}-with-\gl{pl} \gl{1}-be-\gl{npst}//
\glft \qu{I am with you all.}//
\endgl
\xe
%
%Interestingly enough, the verb \qu{to be} only shows \obj{w-} in its \obj{a} root allomorph, but not in the \obj{et͡ʃi} root allomorph, where it has \obj{j-} \exref{car1y.mivida-12}.
%In a somewhat foreshadowing move, I will note that \PTar \rc{(ət)epɨ} \qu{to come} was also affected by the \carijo extension, as seen in \exref{car1y.car-18}.
%As discussed in \cref{sec:taranoan}, this verb preserves \rc{w-} in \akuriyo and \trio \exref{tri-105}.
%
%\pex<car1y>\carijo
%\a<mivida-12>
%\begingl
%\glpreamble iretibə et͡ʃinəme gərə jet͡ʃiɨ//
%\gla ireti-bə et͡ʃi-nə=me gərə j-et͡ʃi-ɨ//
%\glb then-from be-\gl{inf}=\gl{attrz} still \gl{1}-be-\gl{pfv}//
%\glft \qu{Then I was already grown up.} \parencite[][177]{robayo1989rame}//
%\endgl
%\a<car-18>
%\begingl
%\gla əji-wa-e j-eh-ɨ//
%\glb \gl{2}-search-\gl{sup} \gl{1}-come-\gl{pfv}//
%\glft \qu{I came looking for you.} \parencite[][102]{guerrero2019carijo}//
%\endgl
%\xe
%
%\ex<tri-105>\trio \parencite[][337]{triocarlin2004}\\
%\begingl
%\gla ene w-əe//
%\glb see.\gl{sup} \gl{1}\gl{s_a_}-come//
%\glft \qu{I came to see him/her.}//
%\endgl
%\xe

\subsection{\yukpa \obj{j-}}
\label{sec:yukpa}
\yukpa has lost most of its \setone constructions, mostly employing innovative ones \parencite{meira2006syntactic}.
It preserves the \setone prefixes in the immediate past, where the \gl{1}\gl{s_p_} marker appears to have been extended to \gl{s_a_} verbs, as evidenced by the paradigms in \cref{tab:yukreg}.
The loss of split-\gl{s} in favor of the \gl{1}\gl{s_p_} marker is accompanied by the \gl{2}\gl{s_a_} marker \obj{m(ɨ)-} displacing \gl{2}\gl{s_p_} \rc{ə(j)-}, and \gl{1+2} being lost as an inflectional value.
%It has lost the split-\gl{s} system in general

@@

The normal intransitive first person marker is \obj{j(ɨ)-}, including those with clear reflexes of \detrz, like \obj{otum} \qu{to wash self} in \cref{tab:yukreg}.
The analysis that this is a reflex of the \gl{1}\gl{s_p_} marker \rc{u(j)-} is supported by the same form occurring in \gl{3}>\gl{1} scenarios \exref{yukpatr.yuk-5}.

\pex<yukpatr>\yukpa \parencite[][139]{meira2006syntactic}
\a<yuk-5>
\begingl
\gla aw j-esare//
\glb \gl{1}\gl{pro} \gl{3}>\gl{1}-see//
\glft \qu{S/he saw me.}//
\endgl
\a<yuk-1>
\begingl
\gla aw {\normalfont ∅}-esare//
\glb \gl{1}\gl{pro} \gl{1}>\gl{3}-see//
\glft \qu{I saw it.}//
\endgl
\xe
On the other hand, \gl{1}>\gl{3} scenarios are zero-marked \exref{yukpatr.yuk-1}.
Since \PC \gl{1}\gl{s_a_} \rc{w(ɨ)-} was extended to \gl{1}>\gl{3} scenarios in most languages \parencite[81--82]{gildea1998}, and since it is prone to phonological erosion across the family \pcref{sec:pekodian,sec:waiwaian,sec:akuriyo}, we argue that the zero in \gl{1}>\gl{3} scenarios is in fact the \yukpa reflex of \rc{w-}.
The same zero marking is attested for a single intransitive verb: \obj{to} \qu{to go} \exref{yuk-7}.
Based on regular C-initial verbs taking \obj{jɨ-}, like \qu{to sleep} in \exref{yukpaintr}, it is clear that also C-initial \obj{to} \qu{to go} preserved the old \gl{1}\gl{s_a_} marker \rc{w(ɨ)-}, which was lost due to phonological erosion.

>>>>

The V-initial nature of \qu{to go} is evidenced in its Xinguan forms, while \bakairi \phon{\rc{wɨ}}{\obj{u}} muddied the morpheme boundary; other forms are V-initial \pcref{sec:go}.
The \ikpeng form \obj{aran} is compatible with our reconstruction \rc{ɨtən}, when one considers that \ikpeng \obj{a} is an attested outcome of \rc{ə}.\footnote{\begin{inlinelist}
 \item \obj{akari} \qu{dog} in \cref{tab:pxinw} above
 \item \obj{anma} \qu{path} \parencite[24]{ikpengpacheco2001} from \PC \rc{ətema} \parencite[12]{gildea2007greenberg}
 \item \obj{jaj} \qu{tree} \parencite[98]{ikpengpacheco2001} from \PC \rc{jəje}
 \end{inlinelist}.}
This attested change of \rc{ə} to \obj{a} need only be preceded by a assimilatory lowering of initial \rc{ɨ} to \rc{ə}, to yield the form \obj{aran} from \rc{ɨtən}.
Other \ikpeng reflexes of \qu{to go} offer evidence for the suggested intermediate stage \rc{\underline{ə}t\underline{ə}n}: \obj{\underline{e}r\underline{o}-lɨ} \qu{s/he went} \parencite[25]{ikpengpacheco2001}.

@@

\pex<car1w>\carijo \parencite[][5, 42]{guerrero2016karihona}
\a<car-24>
\begingl
\gla wɨ-tə-e=rehe//
\glb \gl{1}-go-\gl{npst}=\gl{frust}//
\glft \qu{I almost go (but I am not going to go).}//
\endgl
\a<car-25>
\begingl
\gla əji-marə-ne w-a-e//
\glb \gl{2}-with-\gl{pl} \gl{1}-be-\gl{npst}//
\glft \qu{I am with you all.}//
\endgl
\xe
%
Further, the verb \obj{ka} \qu{to say} has a zero-marked first-person form \exref{car-33}.
%We interpret this ∅ as a reflex of \rc{wɨ-}, a result of irregular phonological erosion.
Based on other C-initial verbs like \obj{tə} \qu{to go} or \obj{tuda} \qu{to arrive}, one would either expect \obj{wɨ-} or \obj{ji-}.
We analyse this ∅ as a reflex of \rc{wɨ-}, primarily based on the (albeit more regular) loss of \rc{w} in \ikpeng and \hixka, and the presumedly higher propensity of an irregular marker for idiosyncratic phonological erosion.
Further, one may suggest the difference to C-initial \obj{tə} \qu{to go} to result from that verb's former V-initial nature \pcref{sec:go}.

\ex<car-33>\carijo \perscomm{David Felipe Guerrero-Beltran}\\
\begingl
\glpreamble dëmëmara kae ëwï iya//
\gla n-tə-mə=mara ∅-ka-e əwɨ i-ja//
\glb \gl{3}-go-\gl{pst}=\gl{dub} \gl{1}-say-\gl{npst}.\gl{cert} \gl{1}\gl{pro} \gl{3}-\gl{obl}//
\glft \qu{“Did s/he leave?”, I say to him.}//
\endgl
\xe

%
%Interestingly enough, the verb \qu{to be} only shows \obj{w-} in its \obj{a} root allomorph, but not in the \obj{et͡ʃi} root allomorph, where it has \obj{j-} \exref{car1y.mivida-12}.
%In a somewhat foreshadowing move, I will note that \PTar \rc{(ət)epɨ} \qu{to come} was also affected by the \carijo extension, as seen in \exref{car1y.car-18}.
%As discussed in \cref{sec:taranoan}, this verb preserves \rc{w-} in \akuriyo and \trio \exref{tri-105}.
%
%\pex<car1y>\carijo
%\a<mivida-12>
%\begingl
%\glpreamble iretibə et͡ʃinəme gərə jet͡ʃiɨ//
%\gla ireti-bə et͡ʃi-nə=me gərə j-et͡ʃi-ɨ//
%\glb then-from be-\gl{inf}=\gl{attrz} still \gl{1}-be-\gl{pfv}//
%\glft \qu{Then I was already grown up.} \parencite[][177]{robayo1989rame}//
%\endgl
%\a<car-18>
%\begingl
%\gla əji-wa-e j-eh-ɨ//
%\glb \gl{2}-search-\gl{sup} \gl{1}-come-\gl{pfv}//
%\glft \qu{I came looking for you.} \parencite[][102]{guerrero2019carijo}//
%\endgl
%\xe
%
%\ex<tri-105>\trio \parencite[][337]{triocarlin2004}\\
%\begingl
%\gla ene w-əe//
%\glb see.\gl{sup} \gl{1}\gl{s_a_}-come//
%\glft \qu{I came to see him/her.}//
%\endgl
%\xe

\subsection{\yukpa \obj{j-}}
\label{sec:yukpa}
\yukpa has lost most of its \setone constructions, mostly employing innovative ones \parencite{meira2006syntactic}.
It preserves the \setone prefixes in the immediate past, where the \gl{1}\gl{s_p_} marker appears to have been extended to \gl{s_a_} verbs, as evidenced by the paradigms in \cref{tab:yukreg}.
The loss of split-\gl{s} in favor of the \gl{1}\gl{s_p_} marker is accompanied by the \gl{2}\gl{s_a_} marker \obj{m(ɨ)-} extending to \gl{s_p_} verbs, and \gl{1+2} being lost as an inflectional value.
%It has lost the split-\gl{s} system in general

@@

The normal intransitive first person marker is \obj{j(ɨ)-}, including those with clear reflexes of the detransitivizer \detrz, like \obj{otum} \qu{to wash self} in \cref{tab:yukreg}.
The analysis that this is a reflex of the \gl{1}\gl{s_p_} marker \rc{u(j)-} is supported by the same form occurring in \gl{3}>\gl{1} scenarios \exref{yukpatr.yuk-5}.

\pex<yukpatr>\yukpa \parencite[][139]{meira2006syntactic}
\a<yuk-5>
\begingl
\gla aw j-esare//
\glb \gl{1}\gl{pro} \gl{3}>\gl{1}-see//
\glft \qu{S/he saw me.}//
\endgl
\a<yuk-1>
\begingl
\gla aw {\normalfont ∅}-esare//
\glb \gl{1}\gl{pro} \gl{1}>\gl{3}-see//
\glft \qu{I saw it.}//
\endgl
\xe
On the other hand, \gl{1}>\gl{3} scenarios are zero-marked \exref{yukpatr.yuk-1}.
Since \PC \gl{1}\gl{s_a_} \rc{w(ɨ)-} was extended to \gl{1}>\gl{3} scenarios in most languages \parencite[81--82]{gildea1998}, and since it is prone to phonological erosion across the family \pcref{sec:pekodian,sec:waiwaian}, we argue that the zero in \gl{1}>\gl{3} scenarios is in fact the \yukpa reflex of \rc{w-}.

In intransitive verbs, this first-person zero marking is attested only for \obj{to} \qu{to go} \exref{yuk-7}.
It contrasts with regular C-initial verbs taking \obj{jɨ-}, like \qu{to sleep} in \cref{tab:yukreg}.
Thus, we conclude that the extension of \obj{j-} in \yukpa only stopped short of \obj{to} \qu{to go}, which preserves a phonologically reduced reflex of \rc{wɨ-}.
